---
title: "JIBE Melbourne Mode Choice Preparation and Analysis"
format: gfm
execute:
  # no data is to be included in this document, unless intentionally over-ridden
  output: false 
knitr:
  opts_chunk: 
    collapse: true
---

## Background

To conduct the JIBE mode choice modelling for Melbourne requires data preparation using travel survey data. The analysis draws on the [Victorian Integrated Survey of Travel and Activity](https://www.vic.gov.au/victorian-integrated-survey-travel-and-activity) (VISTA[^1]) for 2012-20, used with permission from the Victorian Department of Transport.

The analysis is conducted for the JIBE project by Carl Higgs in August/September 2024, in coordination with Dr Qin Zhang, Corin Staves and Dr Belen Zapata-Diomedi.

It expands on an [earlier mode choice analysis](https://github.com/carlhiggs/multimodal_analysis_example) demonstration using the VISTA travel survey using the [Rapid Realisting Routing with R5 (r5r)](https://ipeagit.github.io/r5r/) routing engine, conducted by Carl Higgs for the JIBE project in March 2022 on behalf of Dr Tayebeh Saghapour.  This was subsequently [adapted](https://github.com/jibeproject/odCalculationsMelbourne) by Dr Alan Both for the JIBE project in February 2024.

The purpose of this analysis is to create appropriate data to inform travel demand generation using the [Microscopic Transport Orchestrator (MITO)](https://www.mos.ed.tum.de/tb/forschung/models/travel-demand/mito/) model by Dr Qin Zhang, [transport simulation modelling](https://github.com/jibeproject/matsim-jibe) by Corin Staves, and [microsimulation of downstream health impacts](https://github.com/jibeproject/health_microsim) related to mode choice and environmental exposures by Dr Belen Zapata-Diomedi, Dr Ali Abbas and Steve Pemberton.

A Quarto markdown document [`JIBE_Melbourne_Mode_Choice.qmd`](JIBE_Melbourne_Mode_Choice.qmd) will be used to document the analysis and updated as the project progresses.  This shall also be rendered as a GitHub-Flavoured-Markdown document [`JIBE_Melbourne_Mode_Choice.md`](JIBE_Melbourne_Mode_Choice.md) for convenient online viewing.

Code (at least at first) will draw on example code prepared by Dr Qin Zhang and Corin Staves, adapting as required for use with the VISTA travel survey.

No data or data-related outputs will be included in this document or repository.  By default, output is set to False.  For non-sensitive aspects, e.g. displaying the `sessionInfo()` after running analysis, this may be over-ridden.

## Status
27 August 2024: commenced, in progress

## System environment set up

```{r}
rm(list = ls()) # clear memory
```

Project dependencies are describe in the [`renv.lock`](./renv.lock) file; see [renv](https://rstudio.github.io/renv/) for more information.  Instructions on installing dependencies using an `renv` lock file are [here](https://rstudio.github.io/renv/articles/renv.html#installing-packages).

```{r}
library(conflicted) # to explicitly handle Tidyverse conflicts https://stackoverflow.com/a/75058976
library(tidyverse)
library(fastDummies)

conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
```

## Classification of trips

Trips will be classified using a standard abbreviation schema, as advised by Dr Qin Zhang and Corin Staves [^2] [^3] [^4]

| Classification | Description |
|:---------------|:------------|
| HBW            | Home based work |
| HBE            | Home based education |
| HBA            | Home based accompanying/escort trip |
| HBS            | Home based shopping |
| HBR            | Home based recreational |
| HBO            | Home based other (e.g. health care, religious activity, visit friend/family) |
| NHBW           | Non-home based work (e.g. from workplace to restaurant) |
| NHBO           | Non-home based other (e.g. from supermarket to restaurant) |
| RRT            | Round Trip |

## Data preparation
### Read data
```{r}
data <- c(
  'H_VISTA_1220_Coord.csv',
  'JTE_VISTA_1220_Coord.csv',
  'JTW_VISTA_1220_Coord.csv',
  'P_VISTA_1220_Coord.csv',
  'S_VISTA_1220_Coord.csv',
  'T_VISTA_1220_Coord.csv'
)
survey<-list()
for (d in data) {
  survey[[sapply(strsplit(d,split='_',1),`[`,1)]]<-read_csv(glue::glue('../../{d}')) 
}
survey
```

### Check data, ensuring that dataset IDs are unique
```{r}
# Person identifier must uniquely identify persons (it does; there are 82,118 unique persons)
table(duplicated(survey$P$persid))
stopifnot(!any(duplicated(survey$P$persid)))

# Trip identifier must uniquely identify trips (it does not)
table(duplicated(survey$T$tripid))

# Look at duplicate tripids (4,104 are NA)
survey$T[duplicated(survey$T$tripid),]

# I visually checked the CSV file and confirmed that these rows just consist of commas
# This can occur if someone exports a CSV from Excel that inadvertently includes blank rows
# I am surprised that the read csv default 'skip_empty_rows = TRUE' did not deal with this.

# Omit NA tripid rows from tripid dataset
survey$T <- survey$T %>% filter(!sapply(tripid, is.na))

# Trip id must be unique  (now, it is; there are 221,819 unique trips)
stopifnot(!any(duplicated(survey$T$tripid)))

# Household ID must uniquely identify households (it does; there are 32,133 households)
table(duplicated(survey$H$hhid))
stopifnot(!any(duplicated(survey$H$hhid)))
```

### Merge data on trips, persons and households
Left joining households to persons, and left joining that to the trip dataset so we have trips>persons>households, respectively joined using their unique identifiers.

```{r}
trips <- survey$T %>% left_join(survey$P  %>% left_join(survey$H, by='hhid'), by='persid')
```

### List columns present in the merged Trip dataset

```{r}
#| output: true
trips %>% colnames()
```

## Assign trip purpose

## Attach travel time 

## Filter out invalid trips records 

## Deal with intrazonal trips
For Manchester there were a substantial number of intrazonal trips, having origin and destination are recorded with the same output area (OA).

For Melbourne, we need to check if intrazonal trips exist, sharing identical origin and destination coordinates.

## Write to CSV

## MORE ANALYSIS TO FOLLOW; THIS IS NOT COMPLETE




## System information for the above analysis

The following information records the version of R used for this analysis:
```{r}
#| output: true
sessionInfo()
```



[^1]: Victorian Government Department of Transport. 2022. Victorian Integrated Survey of Travel and Activity 2012-2020. https://www.vic.gov.au/victorian-integrated-survey-travel-and-activity
[^2]: Ortúzar JdD and Willumsen LG (2011) Modelling Transport. Chichester: John Wiley & Sons, Ltd
[^3]: Staves, Corin. (2020). Physical Activity Assessment and Modelling using Household Travel Surveys. 10.13140/RG.2.2.14307.84009. 
[^4]: Staves C, Zhang Q, Moeckel R, et al. (2023) Integrating health effects within an agent-based land use and transport model. J Transp Health 33: 101707.
